Independent discovery of a nulling pulsar with unusual sub-pulse drifting properties with the Murchison Widefield Array

### 2022-04-27 paper/referee_report_1/response.md

4. Which bright source was used for phase or amplitude calibration? Is it possible to convert the flux into absolute amplitude in the figures instead of arbitrary unit?

  * On inspection, it turns out that all of our observations were calibrated on 3C444. I have edited the text to read "Each observation was individually calibrated using observations of 3C444 taken within ∼2 hours of the respective target observations. The calibration solutions were obtained using the Real Time System software (Mitchell et al. 2008)."
  * Getting reliable absolute flux calibration is challenging for the MWA because of its large, complex primary beam. A fuller investigation of the absolute brightness of the pulsar is intended for a follow-up paper, for which we have also recently acquired observations at higher frequencies (uGMRT), and which we will use for spectral analysis.

5. Please clarify the technical principle of the PSRCHIVE's pdmp to determine period and DM.

  * The following text has been added to Section 2.2: "This routine performs a brute-force grid search in both period and DM parameter space, and returns the period and DM that yields the highest profile signal-to-noise."

@@

14. The LRFS in Figure 6 clearly presents the drifting feature at a frequency of ~0.03 cycles/period in the on-pulse window. In addition, a wide modulation feature with frequency ranging from 0.05-0.1 cycles/period is detected in the leading emission component. The corresponding feature with weak power in the 2DFS is also discernible.

  * These extra details are now more explicitly spelled out in the caption to the LRFS/2DFS figure. We have also expanded slightly on the interpretation of the diffuse component (as a possible connection to Mode B) in the last part of Section 3.2.4.

15. The polarized pulse profiles for different drift modes provide an important clue to reveal the triggering mechanism of mode changing. Is there any difference between averaged pulse profiles by integrating pulses for different drift modes?

  * Unfortunately, we do not yet have reliable polarization for these data sets, but intend to include them in the planned followup paper.
  * We plotted, but have not included, the modal profiles. Visually, there is no significant difference between the profiles of the different modes. The limiting factor here is the relative paucity of Mode B sequences, making the Mode B profiles too noisy to meaningfully compare with the Mode A profiles. However, to the extent we are able to say, they appear to have the same basic shape (two just-resolved components, with the leading component slightly brighter than the trailing component.

@@

16. The observed different subpulse drift modes and the slowly changing in drift rate may be an indication of a local change in the electromagnetic field configuration in the gap. A lot of theoretical modes have been proposed, such as van Leeuwen et al. 2003, A&A, 399, 223; Smith et al. 2005, A&A, 440, 683; Yuen, 2019, MNRAS, 486, 2011.

  * This is indeed our current feeling, and we have amended the relevant paragraph in the Discussion slightly to include the wording suggested by the referee. We have included the van Leeuwen and Yuen references, but could not identify the Smith reference.

@@

17. To our knowledge, no model can satisfactorily explain the observed subpulse drift characteristics for different pulsars. In the future, the multi-frequency study will be required.

  * We whole-heartedly agree! Our next study plans to include both GMRT and Parkes data, covering a wide frequency range.

### 2022-04-27 paper/main.tex
Added a response to the pdmp question.

Lacking a timing solution, we used PSRCHIVE's \texttt{pdmp} routine to determine the best period ($P$) and DM for each observation independently, and the weighted averages over the four observations were calculated (where the reported uncertainties were used to weight the individual measurements).
The values thus derived were $P = 1.306150 \pm 0.000005\,$s and $\text{DM} = \psrdm \pm \psrdmerr\,$\dmunit.
This simple estimate does not take the period derivative into account (in fact, it implicitly assumes $\dot{P} = 0$), and we note that a sufficiently large $\dot{P}$ would cause the period to drift significantly over the time period spanned by our four MWA observations ($\sim$ 1.5\,yr).
However, the pulse stacks (e.g.\ Fig. \ref{fig:pulsestacks}) folded on the above period showed no detectable slope, which we estimate would be discernible if the pulse window changed by more than $20\,$ms over the course of the observation.
Given this, we place a conservative upper limit of $|\dot{P}| \le 10^{-13}$\,s\,s$^{-1}$.

@@

All of these complex drifting behaviors present a natural challenge to the carousel model, whose most basic formulation predicts only a single stable drifting mode, due to the expected stability of the underlying electric and magnetic fields that generate the carousel motion.
Nevertheless, many of the above effects can be successfully explained with the carousel model by invoking aliasing effects that arise due to beating between the stellar rotation rate and the carousel's rotation.
In the presence of aliasing, multiple drift modes can be explained if the number of sparks in the carousel changes, even if the carousel speed itself doesn't change.
This idea has been invoked to explain the multiple drift rates of B1918$+$19 \citep{Rankin2013}, B1819$-$22 \citep{Joshi2017,Janagal2022}, and B0031$-$07 \citep{McSweeney2019a}.
Aliasing can also ``amplify'' the variability of the drift rate if the ratio of stellar rotation and carousel rotation is very close to a ratio of small integers.
That is, a small change in the magnetospheric conditions near the stellar surface (where the sparks reside) can appear to the observer as a relatively large change in the drift rate.
\citet{VanLeeuwen2012} elucidated the connection between the accelerating potential within the polar gap and the carousel behavior, and found that the variability of B0826$-$34's drift rate can be explained in this way.

>>>>

Lacking a timing solution, we used PSRCHIVE's \texttt{pdmp} routine to determine the best period ($P$) and DM for each observation independently. {\bf This routine performs a brute-force grid search in both period and DM parameter space, and returns the period and DM that yields the highest profile signal-to-noise}. The weighted averages {\bf of both period and DM (respectively)} over the four observations were calculated, {\bf with the uncertainties reported by \texttt{pdmp} being} used to weight the individual measurements.
The values thus derived were $P = 1.306150 \pm 0.000005\,$s and $\text{DM} = \psrdm \pm \psrdmerr\,$\dmunit.
This simple estimate does not take the period derivative into account (in fact, it implicitly assumes $\dot{P} = 0$), and we note that a sufficiently large $\dot{P}$ would cause the period to drift significantly over the time period spanned by our four MWA observations ($\sim$ 1.5\,yr).
However, the pulse stacks (e.g.\ Fig. \ref{fig:pulsestacks}) folded on the above period showed no detectable slope, which we estimate would be discernible if the pulse window changed by more than $20\,$ms over the course of the observation.
Given this, we place a conservative upper limit of $|\dot{P}| \le 10^{-13}$\,s\,s$^{-1}$.

@@

All of these complex drifting behaviors present a natural challenge to the carousel model, whose most basic formulation predicts only a single stable drifting mode, due to the expected stability of the underlying electric and magnetic fields that generate the carousel motion.
Nevertheless, many of the above effects can be successfully explained with the carousel model by invoking aliasing effects that arise due to beating between the stellar rotation rate and the carousel's rotation.
In the presence of aliasing, multiple drift modes can be explained if the number of sparks in the carousel changes, even if the carousel speed itself doesn't change.
This idea has been invoked to explain the multiple drift rates of B1918$+$19 \citep{Rankin2013}, B1819$-$22 \citep{Joshi2017,Janagal2022}, and B0031$-$07 \citep{McSweeney2019a}.
Aliasing can also ``amplify'' the variability of the drift rate if the ratio of stellar rotation and carousel rotation is very close to a ratio of small integers.
That is, a small change in the magnetospheric conditions {\bf (e.g. the local electromagnetic configuration)} near the stellar surface ({\bf in the gap,} where the sparks reside) can appear to the observer as a relatively large change in the drift rate.
\citet{VanLeeuwen2012} elucidated the connection between the accelerating potential within the polar gap and the carousel behavior, and found that the variability of B0826$-$34's drift rate can be explained in this way.
{\bf In contrast, \citet{VanLeeuwen2003} argued that aliasing could \emph{not} be present during the post-null changing drift rate for B0809$+$74.
Whether or not aliasing is included, models for changing drift rates are often discussed in terms of the local magnetospheric conditions changing over the relevant time scales \citep[e.g.][]{VanLeeuwen2003, Yuen2019}.}
